\chapter{Introduction}
\section{Rainmaler Labs}

Rainmaker Labs is the singaporean outsourcing company, specialized in mobile development, currently placed first among the competitors in Singapore and Asia Pacific. 

Rainmaker Labs in Vietnam is the new branch which was established in Feb 2015. Though it's new, but thanks to the politics, cultures and remuneration policy, the offshore branch was able to recruit many talented and experienced individuals, some of them even hold high position in their previous jobs.

\subsection{Company's culture}
Rainmaker Labs is a young campany with young people, so the way it run is refresh to me. There isn't any dress code, not too shady clothes are good enough. Working time starts from 8h30 am, and ends at 5h30 pm, lunch break starts from 12h pm and ends at 1h pm. Everyone has their own seat, but you can move everywhere, even the isolated kitchen corner, if you want to emerge in your thoughts. 

If you have an emergency matter to attend, or you just want to lay down and work on your bed, just give your team's leader and project's leader a call, tell them you want to work remote from home. Just make sure don't make it your habit, since interaction directly between team member is better than calling or chatting through internet. 

\subsection{Teams}
Rainmaker Labs in Vietnam has many teams, such as : product team, web team, android team, iOS team, quantity controller team (QC team), marketing team and project manager team. Each team have their own jobs, like android \& iOS team work on mobile development, QC team make sure that every functionality work right, and followed scope of work. Product team work on company's project (beside outsourcing project, company has its own project), web team work on front-end and back-end. Project manager is in charge of project, and make sure that project is sticked to its time line.

\section{Projects}

Although I was new to Android at that time, infact, I had never touch Android before, but I still managed to convince my seniors to let me participate in company's projects. The first project was the small project, named \textbf{Pedro}, which served at the \textbf{Charle \& Keith Fashionable Awards 2015}. In this project I was able to study about the basic of Android development and some advanced technic.

The second one is a big project. This project is the digital version of Singapore government project, \textbf{Electronic Tourist Refund Scheme} aka \textbf{eTRS}. In this report I will concentrate on the technics, and knownledge which I was able to acquired. 
