\chapter{Software Development Method}

During the devlopment of an application, there are many tools and steps. Below are some important items :

\section{SCRUM}

In Rainmaker Labs, we use \textbf{SCRUM} as our software deployment method. With this method, we could deploy software to the customer as fast as possible, and be closest to customer's expectation. There are some important points in SCRUM such as :

\begin{itemize}
	\item break down the project into small tasks, as small as possible.
	\item estimate the difficulties of each task and give points to them, then each member of team will select their task, base on their capability, such that all the team members have the same amount of points.
	\item during the development process, whenever a member encounter a problem which he couldn't solve, they could always ask for help. Team leader, or someone else who did solve the problem before could give hints to help him resolve his issue.
	\item everyday before starting working, team will have a stand-up meeting for about 10 minutes. Scrum master would hear team member reporting about their processes the previous day, and their planning for today's works. 
	\item after each sprint (about a week), team will demonstrate what they have done to the client, allowing them to follow the development process, and correct the features to their ideal.
	\item after some sprints, when the product is about to finish, the tester team will join and dug in for bug. The development team now will start to fix the reported bug, along with working on their tasks.
\end{itemize}

Sadly in our company, SCRUM is not deployed as 100\% as it means to be. The estimation of tasks is not executed by the whole team. In fact, it was the 2 most experience in our team that broken down and estimated every tasks, turn out that the estimation is not done objectively. Some tasks were over-estimated, some were under-estimated. And the most critical point is that both Android and iOS team have the same point for the same task, which is not true. Since there're tasks that could be done easily in Android while in iOS they have to struggle to make it right, and reverse. 

One more drawback, is that actually in our company, point is equal to hour. So a 4 points task is given 4 hours to complete. This is also not true, since point should be given based on the complexity of the task itself. 

Anyway, it was interested to experience method SCRUM myself, though it was not 100\% it supposed to be. 

\section{JIRA}

JIRA is used for managing task. Project manager could monitor everybody's process by following JIRA. Tester could report every bugs they've met on JIRA, and developer could fix the problems thanks to the details of how to produce such bug. 

\section{GitHub}

To manage code, we use github system (paid version, not free one). Developer will create his own branch for each task in JIRA, and after making sure that everything work right, merge that branch into the main branch. 

\section{Charles}

In mobile development, when interacting with internet, for example when calling API, catching network package is very important, since you can then prepare model associate with each kind of reponse, request. For that reason we used Charles. Charles is a software allowed catching package which go through its port, and helped user analyze package's content detail, from header to body.

\section{Testing}

One of the important phase in developping an application is testing. While working on this project, it became clearer to me how important testing is. One of the strangest cases that I've ever met, is that the application worked fine on my phone (Sony), but crashed on another one (Samsung). Without a tester team, and various kinds of devices, it could be impossible to spot this out. 
